---
title: "07-Supplementary-Analysis"
date: '(`r format(Sys.Date(), "%d %B, %Y")`)'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(broom)
library(flextable)
library(rgdal)
library(sf)
library(sp)
library(spatialreg)
library(spdep)
library(tidyverse)
library(tmap)
```

## Load Data

```{r}
# Read in feeder data

feeders_year <- read.csv(here::here("analysis/data/raw_data/feeders_year.csv")) %>% 
  select(-X)

feeders_year$GRIDID <- as.integer(feeders_year$GRIDID)
```

## Wrangling for models

```{r}
sf_feeders_info <- readRDS(here::here("analysis/data/raw_data/sf_feeders_info.rds"))

sf_feeders_info$GRIDID <- as.integer(sf_feeders_info$GRIDID)
```

```{r}
sf_feeder_area_elec <- readRDS(here::here("analysis/data/derived_data/sf_feeder_area_elec.rds"))
```

```{r}
feeder_area_elec <- sf_feeder_area_elec %>% 
  st_set_geometry(NULL)
```

```{r}
feeder_area_elec <- as.data.frame(feeder_area_elec)
```

```{r}
feeder_area_elec <- feeder_area_elec %>% 
  select(GRIDID, FEEDER_NAM, KE_IBC, KE_REGION, elec_norm_area)
```

```{r}
sf_feeder_population <- readRDS(here::here("analysis/data/derived_data/sf_feeder_population.rds"))

sf_feeder_population$GRIDID <- as.integer(sf_feeder_population$GRIDID)
```

```{r}
feeder_population <- sf_feeder_population %>% 
  st_set_geometry(NULL)
```

### Join Data

```{r}
sf_feeders <- left_join(sf_feeders_info, 
                            feeders_year, 
                            by = c("GRIDID" = "GRIDID",
                                   "FEEDER_NAM" = "FEEDER_NAM",
                                   "KE_IBC" = "KE_IBC",
                                   "KE_REGION" = "KE_REGION"))
```

`geometry` is added to `feeders_year` and then saved as `sf_feeders`.

```{r}
sf_feeders <- left_join(sf_feeders, 
                        feeder_area_elec,
                        by = c("GRIDID" = "GRIDID",
                                   "FEEDER_NAM" = "FEEDER_NAM",
                                   "KE_IBC" = "KE_IBC",
                                   "KE_REGION" = "KE_REGION"))
```

`elec_norm_area` or the electricity density is added to `sf_feeders`.

```{r}
sf_feeders <- left_join(sf_feeders, 
                        feeder_population,
                        by = c("GRIDID" = "GRIDID",
                                   "FEEDER_NAM" = "FEEDER_NAM",
                                   "KE_IBC" = "KE_IBC",
                                   "KE_REGION" = "KE_REGION"))
```

`populationsum` is added to `sf_feeders`.

### Filter Data

Filter criteria = losses > 0. Filters of electricity density are not used here.

```{r}
sf_feeders_filtered <- sf_feeders %>% 
  filter(losses > 0)
```

The filter of `losses > 0` brings it to 1187 feeders from 1258.

### Moran's I for Losses

```{r}

losses_sp <- as(sf_feeders_filtered, 'Spatial')
losses_neighbours <- poly2nb(losses_sp)
losses_weights <- nb2listw(losses_neighbours, 
                           style = "W",
                           zero.policy = T)
losses_lag <- lag.listw(losses_weights, losses_sp$losses)

losses_lag_df <- sf_feeders_filtered %>% 
  add_column(losses_lag = losses_lag)

losses_moran <- moran.test(losses_lag_df$losses, losses_weights, 
                           zero.policy = T)

losses_moran$p.value
```

### OLS Model

```{r}

ols_losses <- lm(losses ~ tot + comRel + resRel + indRel + populationsum + factor(KE_IBC), data = sf_feeders_filtered)

OLS_table <- tidy(ols_losses)

summary(ols_losses)

# Calculate confidence intervals

ciOLS <- as.data.frame(tidy(ols_losses, conf.int = TRUE))

```

```{r}
# Augment model

sf_feeders_filtered <- augment(ols_losses, 
                          data = sf_feeders_filtered) %>% 
  st_as_sf()

```

```{r}
ols_coefficients <- data.frame(coefficients(ols_losses))

# Coeff cleanup
ols_coefficients <- cbind(Names = rownames(ols_coefficients), ols_coefficients)

# Number rows
rownames(ols_coefficients) <- 1:nrow(ols_coefficients)

```

#### Set Weights

```{r}
sf_feeders_filtered_sp <- as(sf_feeders_filtered, 'Spatial')
sf_feeders_filtered_neighbours <- poly2nb(sf_feeders_filtered_sp)
sf_feeders_filtered_weights <- nb2listw(sf_feeders_filtered_neighbours, 
                                        style = "W", 
                                        zero.policy = TRUE)
sf_feeders_filtered$.resid_lag <- lag.listw(sf_feeders_filtered_weights, 
                                            sf_feeders_filtered$.resid)

```

Weights are set on the basis of neighbours. This means that adjacent feeders influence each other. 

```{r}
OLS_moran <- moran.test(sf_feeders_filtered$.resid, 
           sf_feeders_filtered_weights, 
           adjust.n = TRUE, 
           zero.policy = TRUE)

```

### Spatial Lag Model

```{r}
# Rescale variables

rescale_tot <- (scale(as.numeric(sf_feeders_filtered$tot)))
rescale_tot <- as.data.frame(rescale_tot)

# Join rescaled variables

sf_feeders_filtered <- bind_cols(sf_feeders_filtered, rescale_tot)

sf_feeders_filtered <- sf_feeders_filtered %>% 
  rename(rescale_tot = `V1`)
```

```{r}
lag_losses <- lagsarlm(losses ~ rescale_tot + comRel + resRel + indRel + populationsum + factor(KE_IBC),
                 data = sf_feeders_filtered,
                 listw = sf_feeders_filtered_weights,
                 na.action(sf_feeders_filtered_weights),
                 zero.policy = T)

summary(lag_losses, Nagelkerke = T)

# Calculate confidence intervals

ciLag <- as.data.frame(tidy(lag_losses, conf.int = TRUE))

impacts(lag_losses, listw = sf_feeders_filtered_weights)

sf_feeders_filtered$resid_lagsarlm <- residuals(lag_losses)

lag_moran <- moran.test(sf_feeders_filtered$resid_lagsarlm, 
           sf_feeders_filtered_weights, 
           adjust.n = TRUE, 
           zero.policy = TRUE)

lag_moran$p.value
```

```{r}
lag_coefficients <- data.frame(coefficients(lag_losses))

# Coeff cleanup
lag_coefficients <- cbind(Names = rownames(lag_coefficients), lag_coefficients)

# Number rows
rownames(lag_coefficients) <- 1:nrow(lag_coefficients)

```

```{r}
lag_estimates <- summary(lag_losses)$Coef[,1]
lag_estimates <- as.data.frame(lag_estimates)
lag_estimates <- cbind(Names = rownames(lag_estimates), lag_estimates)
rownames(lag_estimates) <- 1:nrow(lag_estimates)


lag_stderror <- summary(lag_losses)$Coef[,2]
lag_stderror <- as.data.frame(lag_stderror)
lag_stderror <- cbind(Names = rownames(lag_stderror), lag_stderror)
rownames(lag_stderror) <- 1:nrow(lag_stderror)


lag_prz <- summary(lag_losses)$Coef[,4]
lag_prz <- as.data.frame(lag_prz)
lag_prz <- cbind(Names = rownames(lag_prz), lag_prz)
rownames(lag_prz) <- 1:nrow(lag_prz)

lag_table <- left_join(lag_estimates, lag_stderror)
lag_table <- left_join(lag_table, lag_prz)

```

### Spatial Error Model

```{r}
error_losses <- errorsarlm(losses ~ rescale_tot + comRel + resRel + indRel + populationsum + factor(KE_IBC),  data = sf_feeders_filtered,
                 listw = sf_feeders_filtered_weights,
                 na.action(sf_feeders_filtered_weights),
                 zero.policy = T)
```

```{r}
summary(error_losses, Nagelkerke = T)
```

```{r}
# Calculate confidence intervals

ciError <- as.data.frame(tidy(error_losses, conf.int = TRUE))

```

```{r}
sf_feeders_filtered$resid_error <- residuals(error_losses)

error_moran <- moran.test(sf_feeders_filtered$resid_error, 
           sf_feeders_filtered_weights, 
           adjust.n = TRUE, 
           zero.policy = TRUE)

error_moran$p.value

error_coefficients <- data.frame(coefficients(error_losses))

# Coeff cleanup
error_coefficients <- cbind(Names = rownames(error_coefficients), error_coefficients)

# Number rows
rownames(error_coefficients) <- 1:nrow(error_coefficients)

```

```{r}
error_estimates <- summary(error_losses)$Coef[,1]
error_estimates <- as.data.frame(error_estimates)
error_estimates <- cbind(Names = rownames(error_estimates), error_estimates)
rownames(error_estimates) <- 1:nrow(error_estimates)


error_stderror <- summary(error_losses)$Coef[,2]
error_stderror <- as.data.frame(error_stderror)
error_stderror <- cbind(Names = rownames(error_stderror), error_stderror)
rownames(error_stderror) <- 1:nrow(error_stderror)

error_prz <- summary(error_losses)$Coef[,4]
error_prz <- as.data.frame(error_prz)
error_prz <- cbind(Names = rownames(error_prz), error_prz)
rownames(error_prz) <- 1:nrow(error_prz)

error_table <- left_join(error_estimates, error_stderror)
error_table <- left_join(error_table, error_prz)

```

## Table of Results

This file contains tables of results obtained from the spatial models.

```{r}
options(digits = 10)
```

```{r}
NL_OLS_table <- OLS_table
```

```{r}
# Recode rows

NL_OLS_table <- NL_OLS_table %>% 
  mutate(term = recode(term, 
                        `(Intercept)` = "Intercept",
                        tot = "Total",
                        comRel = "Commercial %",
                        resRel = "Residential %",
                        indRel = "Industrial %",
                        populationsum = "Population", 
                         `factor(KE_IBC)Baldia` = "Baldia",
                         `factor(KE_IBC)Bin Qasim` = "Bin Qasim",
                         `factor(KE_IBC)Clifton` = "Clifton",
                         `factor(KE_IBC)Defence` = "Defence",
                         `factor(KE_IBC)F.B Area` = "F.B Area",
                         `factor(KE_IBC)Gadap` = "Gadap",
                         `factor(KE_IBC)Garden` = "Garden",
                         `factor(KE_IBC)Gulshan-e-Iqbal` = "Gulshan-e-Iqbal",
                         `factor(KE_IBC)Johar-I` = "Johar-I",
                         `factor(KE_IBC)Johar-II` = "Johar-II",
                         `factor(KE_IBC)Johar II` = "Johar II",
                         `factor(KE_IBC)KIMZ` = "KIMZ",
                         `factor(KE_IBC)Korangi` = "Korangi",
                         `factor(KE_IBC)Landhi` = "Landhi",
                         `factor(KE_IBC)Liaquatabad` = "Liaquatabad",
                         `factor(KE_IBC)Lyari-I` = "Lyari-I",
                         `factor(KE_IBC)Lyari-II` = "Lyari-II",
                         `factor(KE_IBC)Malir` = "Malir",
                         `factor(KE_IBC)Nazimabad` = "Nazimabad",
                         `factor(KE_IBC)North Karachi` = "North Karachi",
                         `factor(KE_IBC)North Nazimabad` = "North Nazimabad",
                         `factor(KE_IBC)Orangi-I` = "Orangi-I",
                         `factor(KE_IBC)Orangi-II` = "Orangi-II",
                         `factor(KE_IBC)Saddar` = "Saddar",
                         `factor(KE_IBC)Shah Faisal` = "Shah Faisal",
                         `factor(KE_IBC)SITE` = "SITE",
                         `factor(KE_IBC)Surjani` = "Surjani",
                         `factor(KE_IBC)Tipu Sultan` = "Tipu Sultan",
                         `factor(KE_IBC)Uthal` = "Uthal"
                         ))

```

```{r}
# round values

NL_OLS_table <- NL_OLS_table %>% 
  mutate(estimate = round(estimate, 5)) %>% 
  mutate(pvalue = round(p.value, 5))

NL_OLS_table <- NL_OLS_table %>% 
  select(term, estimate, pvalue)

NL_OLS_table <- NL_OLS_table %>% 
  rename(Names = term,
         OLSestimates = estimate,
         OLSpvalue = pvalue)

```

```{r}
# Recode rows

ciOLS <- ciOLS %>% 
  mutate(term = recode(term, 
                        `(Intercept)` = "Intercept",
                        tot = "Total",
                        comRel = "Commercial %",
                        resRel = "Residential %",
                        indRel = "Industrial %",
                        populationsum = "Population", 
                         `factor(KE_IBC)Baldia` = "Baldia",
                         `factor(KE_IBC)Bin Qasim` = "Bin Qasim",
                         `factor(KE_IBC)Clifton` = "Clifton",
                         `factor(KE_IBC)Defence` = "Defence",
                         `factor(KE_IBC)F.B Area` = "F.B Area",
                         `factor(KE_IBC)Gadap` = "Gadap",
                         `factor(KE_IBC)Garden` = "Garden",
                         `factor(KE_IBC)Gulshan-e-Iqbal` = "Gulshan-e-Iqbal",
                         `factor(KE_IBC)Johar-I` = "Johar-I",
                         `factor(KE_IBC)Johar-II` = "Johar-II",
                         `factor(KE_IBC)Johar II` = "Johar II",
                         `factor(KE_IBC)KIMZ` = "KIMZ",
                         `factor(KE_IBC)Korangi` = "Korangi",
                         `factor(KE_IBC)Landhi` = "Landhi",
                         `factor(KE_IBC)Liaquatabad` = "Liaquatabad",
                         `factor(KE_IBC)Lyari-I` = "Lyari-I",
                         `factor(KE_IBC)Lyari-II` = "Lyari-II",
                         `factor(KE_IBC)Malir` = "Malir",
                         `factor(KE_IBC)Nazimabad` = "Nazimabad",
                         `factor(KE_IBC)North Karachi` = "North Karachi",
                         `factor(KE_IBC)North Nazimabad` = "North Nazimabad",
                         `factor(KE_IBC)Orangi-I` = "Orangi-I",
                         `factor(KE_IBC)Orangi-II` = "Orangi-II",
                         `factor(KE_IBC)Saddar` = "Saddar",
                         `factor(KE_IBC)Shah Faisal` = "Shah Faisal",
                         `factor(KE_IBC)SITE` = "SITE",
                         `factor(KE_IBC)Surjani` = "Surjani",
                         `factor(KE_IBC)Tipu Sultan` = "Tipu Sultan",
                         `factor(KE_IBC)Uthal` = "Uthal"
                         ))

```

```{r}
# Keep only the term and confidence intervals

ciOLS <- ciOLS %>% 
  select(term, conf.low, conf.high)

# Round the values off

ciOLS <- ciOLS %>% 
  mutate(conf.low = round(conf.low, 5)) %>% 
  mutate(conf.high = round(conf.high, 5))

# Merge the columns into one

ciOLS <- ciOLS %>% 
  unite(OLSCI,
        2:3,
        remove = TRUE,
        sep = ", ")
```

```{r}
# Join Tables

NL_OLS_table <- left_join(NL_OLS_table, ciOLS, by = c("Names" = "term"))
```

```{r}
### Spatial Error Model

NL_error_table <- error_table
```

```{r}
# Recode rows

NL_error_table <- NL_error_table %>% 
  mutate(Names = recode(Names, 
                        `(Intercept)` = "Intercept",
                        rescale_tot = "Total",
                        comRel = "Commercial %",
                        resRel = "Residential %",
                        indRel = "Industrial %",
                        populationsum = "Population",
                         `factor(KE_IBC)Baldia` = "Baldia",
                         `factor(KE_IBC)Bin Qasim` = "Bin Qasim",
                         `factor(KE_IBC)Clifton` = "Clifton",
                         `factor(KE_IBC)Defence` = "Defence",
                         `factor(KE_IBC)F.B Area` = "F.B Area",
                         `factor(KE_IBC)Gadap` = "Gadap",
                         `factor(KE_IBC)Garden` = "Garden",
                         `factor(KE_IBC)Gulshan-e-Iqbal` = "Gulshan-e-Iqbal",
                         `factor(KE_IBC)Johar-I` = "Johar-I",
                         `factor(KE_IBC)Johar-II` = "Johar-II",
                         `factor(KE_IBC)Johar II` = "Johar II",
                         `factor(KE_IBC)KIMZ` = "KIMZ",
                         `factor(KE_IBC)Korangi` = "Korangi",
                         `factor(KE_IBC)Landhi` = "Landhi",
                         `factor(KE_IBC)Liaquatabad` = "Liaquatabad",
                         `factor(KE_IBC)Lyari-I` = "Lyari-I",
                         `factor(KE_IBC)Lyari-II` = "Lyari-II",
                         `factor(KE_IBC)Malir` = "Malir",
                         `factor(KE_IBC)Nazimabad` = "Nazimabad",
                         `factor(KE_IBC)North Karachi` = "North Karachi",
                         `factor(KE_IBC)North Nazimabad` = "North Nazimabad",
                         `factor(KE_IBC)Orangi-I` = "Orangi-I",
                         `factor(KE_IBC)Orangi-II` = "Orangi-II",
                         `factor(KE_IBC)Saddar` = "Saddar",
                         `factor(KE_IBC)Shah Faisal` = "Shah Faisal",
                         `factor(KE_IBC)SITE` = "SITE",
                         `factor(KE_IBC)Surjani` = "Surjani",
                         `factor(KE_IBC)Tipu Sultan` = "Tipu Sultan",
                         `factor(KE_IBC)Uthal` = "Uthal"
                         ))

```

```{r}
# round values

NL_error_table <- NL_error_table %>% 
  mutate(estimates = round(error_estimates, 5)) %>% 
  mutate(prz = round(error_prz, 5))

NL_error_table <- NL_error_table %>% 
  select(-error_estimates, -error_prz, -error_stderror)

```

```{r}
# Recode rows

ciError <- ciError %>% 
  mutate(term = recode(term, 
                        `(Intercept)` = "Intercept",
                        rescale_tot = "Total",
                        comRel = "Commercial %",
                        resRel = "Residential %",
                        indRel = "Industrial %",
                        populationsum = "Population", 
                         `factor(KE_IBC)Baldia` = "Baldia",
                         `factor(KE_IBC)Bin Qasim` = "Bin Qasim",
                         `factor(KE_IBC)Clifton` = "Clifton",
                         `factor(KE_IBC)Defence` = "Defence",
                         `factor(KE_IBC)F.B Area` = "F.B Area",
                         `factor(KE_IBC)Gadap` = "Gadap",
                         `factor(KE_IBC)Garden` = "Garden",
                         `factor(KE_IBC)Gulshan-e-Iqbal` = "Gulshan-e-Iqbal",
                         `factor(KE_IBC)Johar-I` = "Johar-I",
                         `factor(KE_IBC)Johar-II` = "Johar-II",
                         `factor(KE_IBC)Johar II` = "Johar II",
                         `factor(KE_IBC)KIMZ` = "KIMZ",
                         `factor(KE_IBC)Korangi` = "Korangi",
                         `factor(KE_IBC)Landhi` = "Landhi",
                         `factor(KE_IBC)Liaquatabad` = "Liaquatabad",
                         `factor(KE_IBC)Lyari-I` = "Lyari-I",
                         `factor(KE_IBC)Lyari-II` = "Lyari-II",
                         `factor(KE_IBC)Malir` = "Malir",
                         `factor(KE_IBC)Nazimabad` = "Nazimabad",
                         `factor(KE_IBC)North Karachi` = "North Karachi",
                         `factor(KE_IBC)North Nazimabad` = "North Nazimabad",
                         `factor(KE_IBC)Orangi-I` = "Orangi-I",
                         `factor(KE_IBC)Orangi-II` = "Orangi-II",
                         `factor(KE_IBC)Saddar` = "Saddar",
                         `factor(KE_IBC)Shah Faisal` = "Shah Faisal",
                         `factor(KE_IBC)SITE` = "SITE",
                         `factor(KE_IBC)Surjani` = "Surjani",
                         `factor(KE_IBC)Tipu Sultan` = "Tipu Sultan",
                         `factor(KE_IBC)Uthal` = "Uthal"
                         ))

```

```{r}
# Keep only the term and confidence intervals

ciError <- ciError %>% 
  select(term, conf.low, conf.high)

# Round the values off

ciError <- ciError %>% 
  mutate(conf.low = round(conf.low, 5)) %>% 
  mutate(conf.high = round(conf.high, 5))

# Merge the columns into one

ciError <- ciError %>% 
  unite(errorCI,
        2:3,
        remove = TRUE,
        sep = ", ")
```

```{r}
# Join Tables

NL_error_table <- left_join(NL_error_table, ciError, by = c("Names" = "term"))
```

```{r}
### Join Tables

results <- left_join(NL_OLS_table, NL_error_table, by = c("Names" = "Names"))
```

```{r}
### Add model fit stats

Names <- c("Summary Statistics", "Adjusted R-Squared", "Moran's I", "AIC", "Log-likelihood")
OLSestimates <- c(NA, 0.546, 0.200, -1665.0386, 868.5193)
OLSpvalue <- c(NA, NA, NA, NA, NA)
estimates <- c(NA, 0.598, -0.008, -1773.5696, 923.7848)
prz <- c(NA, NA, NA, NA, NA)

modelStats <- data.frame(Names, OLSestimates, OLSpvalue, estimates, prz)

```

Table 1: Results from Spatial Error Model

```{r}
### Viz

NL_error_results <- results %>% 
  slice(1:6)

NL_error_results <- bind_rows(NL_error_results, modelStats)

NL_flex_error_results <- flextable(NL_error_results, col_keys = c("Names", 
                                                    "OLSestimates",
                                                    "OLSpvalue",
                                                    "OLSCI",
                                                    "estimates",
                                                    "prz",
                                                    "errorCI"))

NL_flex_error_results <- colformat_num(NL_flex_error_results, 
                                       col_keys = "OLSpvalue", 
                                       i = ~ OLSpvalue < 0.05,
                                       suffix = "*",
                                       digits = 5)

NL_flex_error_results <- colformat_num(NL_flex_error_results, 
                                       col_keys = "prz", 
                                       i = ~ prz < 0.05,
                                       suffix = "*",
                                       digits = 5)

NL_flex_error_results <- set_header_labels(NL_flex_error_results,
                                      Names = "Term",
                                      OLSestimates = "OLS Model",
                                      OLSpvalue = "OLS Model",
                                      OLSCI = "OLS Model",
                                      estimates = "Spatial Error Model",
                                      prz = "Spatial Error Model",
                                      errorCI = "Spatial Error Model")

NL_flex_error_results <- merge_at(NL_flex_error_results,
                                  i = 1,
                                  j = 2:4,
                                  part = "header")

NL_flex_error_results <- merge_at(NL_flex_error_results,
                                  i = 1,
                                  j = 5:7,
                                  part = "header")

NL_flex_error_results <- add_header_row(NL_flex_error_results,
                                        values = c("",
                                                   "Estimate",
                                                   "p",
                                                   "95% CI",
                                                   "Estimate",
                                                   "Pr(>|z|)",
                                                   "95% CI"),
                                                   top = FALSE)

NL_flex_error_results <- add_footer_lines(NL_flex_error_results,
                                     values = c("* p < 0.05",
                                                "* Pr(>|z|) < 0.05"))

NL_flex_error_results <- align(NL_flex_error_results, 
                          align = "center",
                          part = "header")

NL_flex_error_results <- fontsize(NL_flex_error_results, 
                             part = "header",
                             size = 12)

NL_flex_error_results <- autofit(NL_flex_error_results, add_w = 0, add_h = 0)

NL_flex_error_results <- add_header_lines(NL_flex_error_results,
                                     values = c("Coefficient estimates from different modelling approaches"))

save_as_docx(NL_flex_error_results,
             path = here::here("analysis/07-Sup-Table-of-Results.docx"))
```
